Ontology Matching with word2vec

### 2016-03-11 Paper/Draft.tex
2 comments

 Three things are required before this web of computers who communicate and understand, this Semantic Web, will come into existence. The first thing is ???. 
 Secondly, it needs to be adopted by humans. They must see the value of these personal assistants that can schedule things for you, that take into account your personal context when searching the web, that understand questions and can ask you for more information that can improve the search. People have to realise that the current search engines are not good enough, and that having to read through many papers to find the one nugget of information or the one connection that you are looking for is not acceptable or necessary.
 Lastly, the different knowledge bases and unstructured texts need to be aligned. This means that softbots should be able to reason about facts that are contained in different domains and documents. This last problem is the one that I will work on in this thesis. Once we can combine the information from different databases and unstructured text, the Semantic Web is technically possible and only needs to be socially accepted before it will become the norm.

@@

\section{Context}
 In this section I will discuss all concepts that are required to understand the study.
 \subsection{The Semantic Web}
 The Semantic Web, or Web 3.0, is a concept of a Web that enhances the User Experience in ways that the current Web can not provide. Web 2.0, the current Web, models the internet as \textit{hubs} (or sites) with a specific purpose and barely any interconnectivity. For example, Facebook is a hub for sharing content with people you consider friends, but if you want to share that content with more people you will have to go to another hub, like imgur or Pinterest.
The Semantic Web, on the other hand, sees web pages as sources of \textit{information} that can be combined whenever the user needs it. This allows not only humans to browse the internet, but also Artificial Intelligences, which will use this information to aid their users.

>>>>

 Two things are required before this web of computers who communicate and understand, this Semantic Web, will come into existence. 
 Firstly, the Semantic Web needs to be adopted by humans. They must see the value of these personal assistants that can schedule things for you, that take into account your personal context when searching the web, that understand questions and can ask you for more information that can improve the search. People have to realise that the current search engines are not good enough, and that having to read through many papers to find the one nugget of information or the one connection that you are looking for is not acceptable or necessary.
 Lastly, the different knowledge bases and unstructured texts need to be aligned. This means that softbots should be able to reason about facts that are contained in different domains and documents. This last problem is the one that I will work on in this thesis. Once we can combine the information from different databases and unstructured text, the Semantic Web is technically possible and only needs to be socially accepted before it will become the norm.

@@

 % This should actually be quite long since the whole context section is probably going to be ~10 pages, so 1 page is still fairly short. With a context too short a lot of information gets lost and it comes across as cluttered.

\section{Context}
% Give an overview of the section
 In this section I will discuss all concepts that are required to understand the study.
 \subsection{The Semantic Web}
 The Semantic Web, or Web 3.0, is a concept of a Web that enhances the User Experience in ways that the current Web can not provide. Web 2.0, the current Web, models the internet as \textit{hubs} (or sites) with a specific purpose and barely any interconnectivity. For example, Facebook is a hub for sharing content with people you consider friends, but if you want to share that content with more people you will have to go to another hub, like imgur or Pinterest.
The Semantic Web, on the other hand, sees web pages as sources of \textit{information} that can be combined whenever the user needs it. This allows not only humans to browse the internet, but also Artificial Intelligences, which will use this information to aid their users.
